SLE martingales in coset conformal field theory

### 2012-05-10 AffineLieAlgebras/SLE/paper.tex
Added one paper to bibliography

For example consider  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models. Then we get perturbation by $\phi_{(2,1)}$ primary field from the action
\begin{equation}
  S=S_{\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}} (\gamma_1,\gamma_2,\alpha,\bar \alpha) - \frac{k\lambda}{2\pi}\int Tr(\gamma_1^{-1} \gamma_2+\gamma_2^{-1}\gamma_1)
\end{equation}

Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off}. Inclusion of a drift term in (\ref{eq:20}) leads to the  appearance of new terms in the martingale condition (\ref{eq:8}).

>>>>

For example consider  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models. Then we get perturbation by $\phi_{(2,1)}$ primary field from the action
\begin{equation}
  S=S_{\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}} (\gamma_1,\gamma_2,\alpha,\bar \alpha) - \frac{k\lambda}{2\pi}\int Tr(\gamma_1^{-1} \gamma_2+\gamma_2^{-1}\gamma_1)
\end{equation}
This perturbation leads to insertion of perturbing operator in all correlation functions

Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off,bauer2009off}. Inclusion of a drift term in (\ref{eq:20}) leads to the  appearance of new terms in the martingale condition (\ref{eq:8}).
